P3692R2: How to Avoid OOTA Without Really Trying

### 2025-07-10 paper/ootavacuous.tex
ootavacuous: Update history and move from D3692R1 to P3692R2
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{document}
\title{D3692R1: How to Avoid OOTA Without Really Trying}

@@

\begin{itemize}
\item	D3692R1 adds contact information, defines ``preserved
	dependencies'' that are a subset of syntactic and a superset of
	semantic dependencies, and makes numerous changes in the name
	of wordsmithing and clarification.
\item	This paper is a condensation of P3064R2 (``How to Avoid OOTA
	Without Really
	Trying'')~\cite{PaulEMcKenney2023P3046R2/OOTAwithoutTrying},
	which was criticized as being overly long.
	Voluminous off-list discussions are reflected.
	It also adds citations and clarifications.
\end{itemize}

>>>>

\begin{document}
\title{P3692R2: How to Avoid OOTA Without Really Trying}

@@

\begin{itemize}
\item	P3692R2 applies feedback from the 2025 Sophia meeting,
	including reworking the requested change to the standard
	in terms of volatile semantics (courtesy of Olivier Giroux),
	states this paper's benefits to other OOTA researchers, and
	updates the author list.
\item	P3692R1 adds contact information, defines ``preserved
	dependencies'' that are a subset of syntactic and a superset of
	semantic dependencies, and makes numerous changes in the name
	of wordsmithing and clarification.
\item	This paper is a condensation of P3064R2 (``How to Avoid OOTA
	Without Really
	Trying'')~\cite{PaulEMcKenney2023P3046R2/OOTAwithoutTrying},
	which was criticized as being overly long.
	Voluminous off-list discussions are reflected.
	It also adds citations and clarifications.
\end{itemize}
